\vspace{3em}

\rule{\textwidth}{1pt}
\\
\textbf{POLICIES}
\begin{itemize}
\item {\bf Acknowledgments: \/} 
  We expect you to make an honest effort to solve the problems individually.  As we sometimes reuse problem set questions from previous years, covered by papers and web pages, we expect the students \textbf{NOT} to copy, refer to, or look at the solutions in preparing their answers (relating to an unauthorized material is considered a violation of the honor principle). Similarly, we expect to not to google directly for answers (though you are free to google for knowledge about the topic). If you do happen to use other material, it must be acknowledged here, with a citation on the submitted solution.
  
\item {\bf Required homework submission format: \/} 
  You can submit homework either as one single PDF document or as handwritten papers. Written homework needs to be provided during the class in the due date, and PDF document needs to be submitted through Tsinghua's Web Learning (\url{http://learn.tsinghua.edu.cn/}) before the end of due date.
  
  It is encouraged you \LaTeX\ all your work, and we would provide a \LaTeX\ template for your homework.

\item {\bf Collaborators: \/}
In a separate section (before your answers), list the names of all people you collaborated with and for which question(s). If you did the HW entirely on your own, \textbf{PLEASE STATE THIS}. Each student must understand, write, and hand in answers of their own.
\end{itemize}
\rule{\textwidth}{1pt}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "ldps1"
%%% End:
